Cooperative Control for Narrow Passage Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station

### 2012-10-11 manuscript.tex
More text. Added a legend to the feasible set figure

@@

To verify the feasible region experimentally, we conducted trials at initial
distances in X meter increments from the window along the edges of the image
frame of the camera. We started each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figure~\ref{fig:flight_paths}.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{figure}

@@

To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from the window along the
edges of the image frame of the camera. We started each trial with an initial
heading perpendicular to the window plane. The results of the experiments are
shown in Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 79\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region (Figure~\ref{flight_paths}), the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending on the PID
tuning and the distance from the camera.
